---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Lab3package

<!-- badges: start -->
<!-- badges: end -->

The goal of Lab3package is to thin the large shape files and convert it into a data frame containing Longitude, Latitude, group, order and NAME_1 or HASC_1 so that you can make a polygon figure colored by region(NAME_1 or HASC_1) using this data frame.

## Installation

You can install the development version of Lab3package from [GitHub](https://github.com/) with:

```{r, eval=FALSE, echo=TRUE}
# install.packages("devtools")
devtools::install_github("JinjiPang/Lab3package")
```

## Example

This is a basic example to show how to use functions in this package to create geometric data frame and some implementations.

```{r data example}
library(Lab3package)
data("Yemen")
```

First, you can download a shape file of a country of your choice. Then, you can either read the file using `sf::read_sf()`first or just use the file path to try the following codes:

#### team_2 

This function will return a data frame with four basic variables, which are long, lat, order, and group.

```{r }
library(tidyverse)

df1 <- team_2(Yemen, 0.1)

df1 %>%
  ggplot(aes(x = long, y = lat, group = group)) + geom_polygon()


```

#### team_5 

This function will return a data frame with five basic variables, which are long, lat, order, group, and HASC_1.


```{r }
library(tidyverse)

df2 <- team_5(Yemen, 0.1)

df2 %>%
  ggplot(aes(x = long, y = lat, group = group)) + geom_polygon(aes(fill = HASC_1))


```


#### team_6 

This function will return a data frame with 14 variables, basically it keeps all the original variables and add three more variables long, lat, and group.


```{r }
library(tidyverse)

df3 <- team_6(Yemen, 0.1)

df3 %>%
  ggplot(aes(x = long, y = lat, group = group)) + geom_polygon(aes(fill = NAME_1))


```



